Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-19 introduction.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}, exhibiting the three main characteristics commonly found in complex networks: 
\begin{enumerate}[\upshape 1)]
\item Broad degree distribution (power-law/scale-free),
\item Strong clustering (community structure),
\item Small path lengths (small world phenomenon).
\end{enumerate}
Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths. \TM{ \RD{Remove this reference, and replace with Abdullah-Bode-Fountoulakis!!!!}
In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
Of course, in this case Nikoloas \& his crew were  first anyway.
Also, regarding "distances", we probably want to mention graph diameter, studied by Kiwi+Mitsche, Friedrich+Krohmer, M\"uller + Staps.
}
Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law} and the number of cliques and the largest clique~\cite{blasius2018cliques}. \PvdH{@All: Does anyone have other suggestions for results to add?}
\TM{ Yes, of course! Everything Nikolaos\& his crew, and I and my crew, and Kiwi-Mitsche have done on this model. This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles \& perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}

@@

\TM{ I vote to remove this next paragraph. Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches. }
We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}. However, this problem is not explicitly addressed in that paper, nor is there any reason to expect these tools to give us the exact expressions as we do derive in this work.

@@

@@

Let $\alpha > \frac{1}{2}$, $\nu > 0$ and define $R_n = 2\log(n/\nu)$. Then the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ is defined as follows:
\begin{enumerate}
\item The vertex set if given by $n$ points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
\begin{equation}\label{eq:def_hyperbolic_point_distribution}
	F_{n,\alpha,\nu}(r) = \begin{cases}
		0 &\mbox{if } r < 0\\
		\frac{\cosh(\alpha r)-1}{\cosh(\alpha R_n) - 1} &\mbox{if } 0 \le r \le R_n\\
		1&\mbox{if } r > R_n
	\end{cases}
\end{equation}
\item Any two vertices $u_i=(r_i,\theta_i)$ and $u_j=(r_j,\theta_j)$ are adjacent if and only if $d_\H(u_i,u_j) \le R_n$, where $d_\H$ denotes the distance in the hyperbolic plane, i.e.
\[
	\cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n),
\]
as follows from the hyperbolic law of cosines.% rule[CITE?].
\TM{ This is only when $r_i+r_j \geq R$! Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}\PvdH{I do not understand this. The hyperbolic law of cosines defines the hyperbolic cosine of the distance between points in terms of hyperbolic cosines and sines of their radii and the cosine of their relative angle:
\[
	\cosh(d_\H(u_i, u_j)) = \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}).
\] 
Since $\cosh$ is strictly monotonically increasing we have that $\cosh(x) \le \cosh(y) \iff x \le y$ and hence 
\begin{align*}
	&d_\H(u_i, u_j) \le R_n \\
	&\iff \cosh(d_\H(u_i, u_j)) \le \cosh(R_n) \\
	&\iff \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n)
\end{align*}
The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$.}
\end{enumerate}

@@

Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ \TM{ Why 3? } where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. To see this let
\[
	b_n = \arg \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|}.
\]
Then $b_n \le a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
\[
	\lim_{n \to \infty} \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|} 
	= \lim_{n \to \infty}\Exp{\left|\frac{c_{\H ,n}(b_n)}{c_\infty(b_n)} - 1\right|} = 0.
\]
The same is true for the result in Corollary~\ref{cor:asymptotic_local_clustering_hyperbolic}.

>>>>

Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}, exhibiting the three main characteristics commonly found in complex networks: 
\begin{enumerate}[\upshape 1)]
\item Broad degree distribution (power-law/scale-free),
\item Strong clustering (community structure),
\item Small path lengths (small world phenomenon).
\end{enumerate}
Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Abdullah et al.~\cite{abdullah2017typical} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths. \TM{
In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
Of course, in this case Nikoloas \& his crew were  first anyway.
Also, regarding "distances", we probably want to mention graph diameter, studied by Kiwi+Mitsche, Friedrich+Krohmer, M\"uller + Staps.
}
Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law} and the number of cliques and the largest clique~\cite{blasius2018cliques}. \PvdH{@All: Does anyone have other suggestions for results to add?}
\TM{ Yes, of course! Everything Nikolaos\& his crew, and I and my crew, and Kiwi-Mitsche have done on this model. This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles \& perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}\PvdH{Great, could you add those to the bib file and mention them here.}

@@

\TM{ I vote to remove this next paragraph. Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches. }\PvdH{I do not mind if we remove the paragraph. However, the results in J\'{u}lias's paper are rigorous so I do not think that is a good reason for removing the paragraph.}
We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}. However, this problem is not explicitly addressed in that paper, nor is there any reason to expect these tools to give us the exact expressions as we do derive in this work.

@@

\PvdH{@Tobias and Markus: I haven't update this section yet since it will also depend on your new proofs. Please update it once you have added these to the paper.}

@@

Let $\alpha > \frac{1}{2}$, $\nu > 0$ and define $R_n = 2\log(n/\nu)$. Then the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ is defined as follows:
\begin{enumerate}
\item The vertex set if given by $n$ points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
\begin{equation}\label{eq:def_hyperbolic_point_distribution}
	F_{n,\alpha,\nu}(r) = \begin{cases}
		0 &\mbox{if } r < 0\\
		\frac{\cosh(\alpha r)-1}{\cosh(\alpha R_n) - 1} &\mbox{if } 0 \le r \le R_n\\
		1&\mbox{if } r > R_n
	\end{cases}
\end{equation}
\item Any two vertices $u_i=(r_i,\theta_i)$ and $u_j=(r_j,\theta_j)$ are adjacent if and only if $d_\H(u_i,u_j) \le R_n$, where $d_\H$ denotes the distance in the hyperbolic plane, i.e.
\[
	\cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n),
\]
as follows from the hyperbolic law of cosines.% rule[CITE?].
\TM{ This is only when $r_i+r_j \geq R$! Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}\PvdH{I do not understand this. The hyperbolic law of cosines defines the hyperbolic cosine of the distance between points in terms of hyperbolic cosines and sines of their radii and the cosine of their relative angle:
\[
	\cosh(d_\H(u_i, u_j)) = \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}).
\] 
Since $\cosh$ is strictly monotonically increasing we have that $\cosh(x) \le \cosh(y) \iff x \le y$ and hence 
\begin{align*}
	&d_\H(u_i, u_j) \le R_n \\
	&\iff \cosh(d_\H(u_i, u_j)) \le \cosh(R_n) \\
	&\iff \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n)
\end{align*}
The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$. There were however some sloppy arguments later in Section~\ref{ssec:coupling_H_P}, regarding the hyperbolic balls, which I corrected.}
\end{enumerate}

@@

Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $2 \le k \le a_n$ \TM{ Why 3? }\PvdH{Should have been $2$ (corrected) since there are no triangles for node with degree less than $2$.} where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. To see this let
\[
	b_n = \arg \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|}.
\]
Then $b_n \le a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
\[
	\lim_{n \to \infty} \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|} 
	= \lim_{n \to \infty}\Exp{\left|\frac{c_{\H ,n}(b_n)}{c_\infty(b_n)} - 1\right|} = 0.
\]
The same is true for the result in Corollary~\ref{cor:asymptotic_local_clustering_hyperbolic}.

### 2019-01-19 paper.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@

@@

@@

\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}}
\author[1]{Nikolaos Fountoulakis}
\author[2]{Pim van der Hoorn}
\author[3]{Tobias M\"{u}ller}
\author[3]{Markus Schepers}

@@

\input{proof_overview}

>>>>

\usepackage{tocloft}

@@

% Redefines the space between sections in the TOC so that the entire thing fits on one page. 
% Comment this out when not using the tocloft package
\setlength{\cftbeforesecskip}{5pt}

@@

%Uncomment the part below to remove all comments
%\renewcommand{\PvdH}[1]{}
%\renewcommand{\TM}[1]{}
%\renewcommand{\MS}[1]{}
%\renewcommand{\NF}[1]{}

@@

\title{Exact asymptotic expressions for local clustering in a hyperbolic model of complex networks. \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}\PvdH{I am not really a fan of the term KPKVB random graph so I implemented the second suggestion.}}
\author[1]{Nikolaos Fountoulakis}
\author[2]{Pim van der Hoorn}
\author[3]{Tobias M\"{u}ller}
\author[3]{Markus Schepers}

@@

\input{proof_overview_finite_k}

\input{proofs_finite_k}

\input{proofs_infinite_k}
